### 2021-07-27 paper/paper.tex
mention wrapping Fortran libraries

In traditional monolithic code bases, it is often necessary to implement a new
feature for all combinations of possible (compile time) options. This effort
can make it hard to experiment with new ideas. In contrast, Julia's dynamic
nature and just-ahead-of-time compiler allow us to implement only the features
that are strictly necessary. For example, if a user wants to simulate a new
physics model only on Cartesian grids with smooth solutions, there is no need
to implement anything for curvilinear coordinates or shock capturing approaches.
In addition, it allows to extend \trixi step by step with new capabilities.
For example, there are ongoing efforts to incorporate summation by parts finite
difference methods via SummationByPartsOperators.jl \cite{ranocha2021sbp} and
more discontinuous Galerkin methods on simplices via StartUpDG.jl\footnote{\url{https://github.com/jlchan/StartUpDG.jl}} in \trixi. This becomes feasible since not every
feature combination needs to be considered and it is totally fine to start with
simple variants on a subset of the available meshes.

\todo{TODO: Mention multiple dispatch} %TODO

@@

FLUXO\footnote{\url{https://gitlab.com/project-fluxo/fluxo}} is an open source
MPI Fortran code implementing discontinuous Galerkin methods on unstructured hex
meshes in three space dimensions for advection diffusion equations. It also
implements the same kind of modern DG methods based on flux differencing
to achieve entropy conservation/dissipation or kinetic energy preservation.
Thus, both \trixi and FLUXO share a common set of features, enabling a reasonable
comparison of their performance.

@@

\todo{TODO: Point out that both codes have features the other ones does not} %TODO

@@

\todo{TODO: Mention also Fortran libraries/codes (KROME, HOHQMesh)} %TODO

>>>>

In traditional monolithic code bases, it is often necessary to implement a new
feature for all combinations of possible (compile time) options. This effort
can make it hard to experiment with new ideas. In contrast, Julia's dynamic
nature, multiple dispatch, and just-ahead-of-time compilation allow us to implement only the features
that are strictly necessary. For example, if a user wants to simulate a new
physics model only on Cartesian grids with smooth solutions, there is no need
to implement anything for curvilinear coordinates or shock capturing approaches.
In addition, it allows to extend \trixi step by step with new capabilities.
For example, there are ongoing efforts to incorporate summation by parts finite
difference methods via SummationByPartsOperators.jl \cite{ranocha2021sbp} and
more discontinuous Galerkin methods on simplices via StartUpDG.jl\footnote{\url{https://github.com/jlchan/StartUpDG.jl}} in \trixi. This becomes feasible since not every
feature combination needs to be considered and it is totally fine to start with
simple variants on a subset of the available meshes, selected via multiple dispatch.

@@

FLUXO\footnote{\url{https://gitlab.com/project-fluxo/fluxo}} is an open source
MPI Fortran code implementing discontinuous Galerkin methods on unstructured hex
meshes in three space dimensions for advection diffusion equations. It also
implements the same kind of modern DG methods based on flux differencing
to achieve entropy conservation/dissipation or kinetic energy preservation.
At the same time, both codes also have features the other one does not, \eg
parabolic equations and MPI in FLUXO or multiple mesh types in \trixi.
Nevertheless, both \trixi and FLUXO share a common set of features, enabling a
reasonable comparison of their performance.

@@

@@

It is also possible to wrap Fortran libraries/tools in Julia. For example, we
have created the wrappers KROME.jl\footnote{\url{https://github.com/trixi-framework/KROME.jl}}
for KROME, a package to embed chemistry in astrophysical simulations
\cite{grassi2014krome}, and HOHQMesh.jl\footnote{\url{https://github.com/trixi-framework/HOHQMesh.jl}}
for HOHQMesh\footnote{\url{https://github.com/trixi-framework/HOHQMesh}}, a high order
hex-quad mesh generator written in Fortran.
